An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-30 draft.tex
Small corrections and merging experiment 1 with the whole section

% Section headers should be headlines. Like "Measuring scalability in
% heterogenous systems", or something like that. Experiment 1 says
% nothing about what's inside (this also applies below) - JJ
\subsection{Experiment 1}
\label{sec:exp1}
% Experiment 1

@@

\begin{table}
    \small
    \caption{Parameters used in the experiments that used five populations
    }
    \label{tab:params:5}
    \vspace{0.25cm}
    \centering
    \small
    \begin{tabular}{|l|c|c|c|c|c|c|}
      \hline
      Dimension        & 2  & 3  & 5  & 10 & 20  & 40  \\ \hline
      Generations      & 40 & 25 & 28 & 50 & 66  & 80  \\ \hline
      Population Size  & 100 & 120 & 120 & 140 & 200 & 250 \\ \hline
      Populations      & 5 & 5 & 5 & 5 & 5  & 5  \\ \hline
      Iterations       & 10 & 20 & 30 & 30 & 30  & 40  \\ \hline  
    \end{tabular}
\end{table}

@@

% Shouldn't this be a subsection of experimental setup? - JJ
\subsection{Hardware}
\label{sec:hardware}

@@

We present the results of the experiments in this section. The effect of a
different number of populations on execution time is reported in  Section
\ref{sec:exp1results}. The results of the performance comparison between homogeneous and
heterogeneous search strategies are presented in Section \ref{sec:exp2results}.

@@

\subsection{Experiment 1}
\label{sec:exp1results}

@@

As expected, in most cases, increasing the number of workers reduces the time
required for the execution of an instance. Mainly when using the same parameters
(number of populations and number of workers ). But, when we compare the two
options, we find some subtle differences: When using one or two
workers, using 5 populations is better in most cases. A 
reason for this could be that the migration of individuals takes more time to
reach the worker. For instance, when a single worker has 10 populations, only
after processing every one of them, it will start receiving mixed populations.  Although, in
all cases, and even a single worker, populations are heterogeneous, this
advantage takes more time to propagate. With four workers, almost the same
results can be achieved regardless of our selection between five or ten
populations. Also, there is not much difference between 4 and 8 workers, when
using five populations. In general, we can observe that keeping a ratio close to
1:1 between the number of workers and populations  better exploits the computing
resources available.
% I don't really understand this too well... JJ
% Also, it might just be that populations are waiting on the queue to
% be processed if there are more sub-populations than workers. The
% fact that 10 subpopulations take more with 1w than 5 subpopulations
% might be due to late startup as you say above, but you need to
% explain it better.

>>>>

% Section headers should be headlines. Like "Measuring scalability in
% heterogenous systems", or something like that. Experiment 1 says
% nothing about what's inside (this also applies below) - JJ
%\subsection{Experiment 1}
%\label{sec:exp1}
% Experiment 1

@@

\begin{table}
    \small
    \caption{Parameters used in the experiments with five populations
    }
    \label{tab:params:5}
    \vspace{0.25cm}
    \centering
    \small
    \begin{tabular}{|l|c|c|c|c|c|c|}
      \hline
      Dimension        & 2  & 3  & 5  & 10 & 20  & 40  \\ \hline
      Generations      & 40 & 25 & 28 & 50 & 66  & 80  \\ \hline
      Population Size  & 100 & 120 & 120 & 140 & 200 & 250 \\ \hline
      Populations      & 5 & 5 & 5 & 5 & 5  & 5  \\ \hline
      Iterations       & 10 & 20 & 30 & 30 & 30  & 40  \\ \hline  
    \end{tabular}
\end{table}

@@

% Shouldn't this be a subsection of experimental setup? - JJ
% \subsection{Hardware}
% \label{sec:hardware}

@@

We present the results of the experiments in this section. The effect of a
different number of populations on execution time is reported in  Section
\ref{sec:exp1results}.
% The results of the performance comparison between homogeneous and
% heterogeneous search strategies are presented in Section \ref{sec:exp2results}.

@@

% \subsection{Experiment 1}
% \label{sec:exp1results}

@@

As expected, in most cases, increasing the number of workers reduces the time
required for the execution of an instance. Mainly when using the same parameters
(number of populations and number of workers). But, when we compare the two
options, we find some subtle differences: When using one or two
workers, using 5 populations is better in most cases. A 
reason for this could be that the migration of individuals takes more time to
reach the worker. For instance, when a single worker has 10 populations, only
after processing every one of them, it will start receiving mixed populations.  Although, in
all cases, and even a single worker, populations are heterogeneous, this
advantage takes more time to propagate. With four workers, almost the same
results can be achieved regardless of our selection between five or ten
populations. Also, there is not much difference between 4 and 8 workers, when
using five populations. In general, we can observe that keeping a ratio close to
1:1 between the number of workers and populations  better exploits the computing
resources available.
% I don't really understand this too well... JJ
% Also, it might just be that populations are waiting on the queue to
% be processed if there are more sub-populations than workers. The
% fact that 10 subpopulations take more with 1w than 5 subpopulations
% might be due to late startup as you say above, but you need to
% explain it better.
